\speculake: Hiding Malware in Speculative Execution

### 2018-08-02 paper/implementation.tex
remove figure 5

\FigTuringSuccess

@@

Our implementation is able to examine the state and current symbol
on the Turing tape and make decisions based on these values as long as they are
in cache. If one of these becomes uncached, one of two things will happen.
First, the speculative gadget may simply fail to report any result back to the
real world, as the uncached read takes too long to return before the speculative
world is squashed by the resolution of the function pointer. Second, the CPU may
\emph{speculate} on the value of the uncached item, which may be incorrect. Of
course, this does not affect the correctness of normal programs, but it does
impact the correctness of our speculative code. In particular, the speculative
gadget will compute using an incorrect value of state or current
symbol, and ultimately report the wrong update.

@@

In order to have confidence the speculative gadget executed with the
correct inputs and reported the computed result correctly, 
we repeat the execution a number of times and look for the value that was
detected as present in the cache most often over all the iterations.

Our Turing implementation discovered that 10 repetitions is sufficient for the
real world to determine the correct value, as the ``hit rate'' for any one
iteration observing the correct value loaded in cache was over 80\%.

We implemented the 5 state Busy Beaver configuration which requires over 47
million steps to complete. Figure~\ref{fig:turing_success} shows the
capabilities of our Turing implementation. We were able to verify that the
speculative world could correctly compute a million instructions with no errors
at a rate of 324 instructions per second.

>>>>

@@

Our implementation is able to examine the state and current symbol on the Turing
tape and make decisions (in the speculative world) based on these values as long
as they are in cache. If one of these becomes uncached, one of two things will
happen. First, the speculative gadget may simply fail to report any result back
to the real world, as the uncached read takes too long to return before the
speculative world is squashed by the resolution of the function pointer. Second,
the CPU may \emph{speculate} on the value of the uncached item, which may be
incorrect. Of course, this does not affect the correctness of normal programs,
but it does impact the correctness of our speculative code. In particular, the
speculative gadget will compute using an incorrect value of state or current
symbol, and ultimately report the wrong update.

@@

We implemented the 5 state Busy Beaver configuration which requires over 47
million steps to complete. In order to have confidence the speculative gadget
executed with the correct inputs and reported the computed result correctly, we
repeat the execution a number of times and look for the value that was detected
as present in the cache most often over all the iterations. We measured the
error rate of our implementation as a function of how many redundant iterations
of the same step. Our Turing implementation discovered that 10 repetitions is
sufficient for the real world to determine the correct value, as the ``hit
rate'' for any one iteration observing the correct value loaded in cache was
over 80\%. Additionally we found that the speculative world could correctly
compute a million instructions with no errors at a rate of 324 instructions per
second.
